Implications of Measurement Errors in Water Use Estimates for Water Management

### 2024-08-14 Writing/manuscript.Rmd
readme added

This section describes the details of the simulation analysis conducted in this article. Our simulation imagines a region with 1000 (denoted as $N$, hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies. Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors. Under each scenario, 1000 rounds of individual simulations are run. In each simulation round, average water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading. The key components of the simluation analysis are presented below.

@@

For all $i \in 1,\dots, N$, the crop-water production function follows the Michelich-Baule functional form presented below(citations).

@@

@@

Three different sets of the distribution of $\eta$ are considered that vary in the degree of heterogeneity in $\eta$: low, medium, and high. For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased.

For a given scenario, the 1000 individual simulation rounds differ only in the realization of randomly drawn values of $\eta$. A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in Figure \@ref(fig:dist-eta).

## Water use under a quota system

Under both water and proxy quota systems, the same amount of quota is allocated to all the farmers. (this is realistic with insufficient information available to the administrator). For a given water quota of $\overline{w}$, farmer $i$'s water use would be $min\{w^*, \overline{w}\}$. Under the proxy quota system, the same amount of proxy quota ($\overline{p}$) is allocated to all the farmers. However, the effective limit on water use varies by farmer. Given the proxy quota of $\overline{p}$, the effective water use limit for farmer $i$ is $\overline{p} / \eta_i$, and uses $min\{w^*, \overline{p} / \eta_i\}$.

@@

## Water use under a trading system

@@

The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .

>>>>

This section describes the details of the simulation analysis conducted in this article. Our simulation imagines a region with 1000 (denoted as $N$, hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies. Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors. Under each scenario, 1000 rounds of individual simulations are run. In each simulation round, measurement errors are drawn randomly for the individual farmers, and then average (across the farmers) water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading. The summary of the 1000 simulation rounds. The key components of the simluation analysis are presented below.

@@

For all faemers $i \in 1,\dots, N$, the crop-water production function follows the Michelich-Baule functional form presented below(citations).

@@

where $y$ is corn yield (kg/ha), $w$ is water use (mm), and $\phi$, $\alpha$, and $\beta$ are model parameters that govern how corn yield responds to water use.

@@

Three different sets of the distribution of $\eta$ are considered that vary in the degree of heterogeneity in $\eta$: low, medium, and high. For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased. A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in Figure \@ref(fig:dist-eta).

## Water use under quota and trading systems

Under both water and proxy quota systems without trading, the same amount of quota is allocated to all the farmers. (this is realistic with insufficient information available to the administrator). For a given water quota of $\overline{w}$, farmer $i$'s water use would be $min\{w^*, \overline{w}\}$. Under the proxy quota system, the same amount of proxy quota ($\overline{p}$) is allocated to all the farmers. However, the effective limit on water use varies by farmer. Given the proxy quota of $\overline{p}$, the effective water use limit for farmer $i$ is $\overline{p} / \eta_i$, and uses $min\{w^*, \overline{p} / \eta_i\}$.

@@

@@

The datasets created in this article are all computer-generated using R (citation). All the codes and datasets are available at [this GitHub repository](https://github.com/tmieno2/Measurement-Error-Water-Management). Instructions for reproducing all the outputs presented in this article are provided at the bottom of the page.

### 2024-08-14 Writing/manuscript.tex
readme added

This section describes the details of the simulation analysis conducted in this article. Our simulation imagines a region with 1000 (denoted as \(N\), hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies. Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors. Under each scenario, 1000 rounds of individual simulations are run. In each simulation round, average water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading. The key components of the simluation analysis are presented below.

@@

For all \(i \in 1,\dots, N\), the crop-water production function follows the Michelich-Baule functional form presented below(citations).

@@

@@

Three different sets of the distribution of \(\eta\) are considered that vary in the degree of heterogeneity in \(\eta\): low, medium, and high. For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)), meaning that water use estimation is ubiased.

For a given scenario, the 1000 individual simulation rounds differ only in the realization of randomly drawn values of \(\eta\). A sample of the empirical (realized) distribution of \(\eta\) for each of the sets is presented in Figure \ref{fig:dist-eta}.

\subsection{Water use under a quota system}\label{water-use-under-a-quota-system}

Under both water and proxy quota systems, the same amount of quota is allocated to all the farmers. (this is realistic with insufficient information available to the administrator). For a given water quota of \(\overline{w}\), farmer \(i\)'s water use would be \(min\{w^*, \overline{w}\}\). Under the proxy quota system, the same amount of proxy quota (\(\overline{p}\)) is allocated to all the farmers. However, the effective limit on water use varies by farmer. Water and proxy are assumed to follow the following relationship for farmer \(i\),

\begin{equation}
w = \eta_i \cdot p
\end{equation}

Given the proxy quota of \(\overline{p}\), the effective water use limit for farmer \(i\) is \(\overline{p} / \eta_i\), and uses \(min\{w^*, \overline{p} / \eta_i\}\).

@@

\subsection{Water use under a trading system}\label{water-use-under-a-trading-system}

@@

\subsection{Simulations}\label{simulations}

We have nine sets of scenarios: three levels of heterogeneity in optimal water use

1000 rounds of simulations were run

. In each of the rounds,

@@

The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .

>>>>

This section describes the details of the simulation analysis conducted in this article. Our simulation imagines a region with 1000 (denoted as \(N\), hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies. Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors. Under each scenario, 1000 rounds of individual simulations are run. In each simulation round, measurement errors are drawn randomly for the individual farmers, and then average (across the farmers) water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading. The summary of the 1000 simulation rounds. The key components of the simluation analysis are presented below.

@@

For all faemers \(i \in 1,\dots, N\), the crop-water production function follows the Michelich-Baule functional form presented below(citations).

@@

where \(y\) is corn yield (kg/ha), \(w\) is water use (mm), and \(\phi\), \(\alpha\), and \(\beta\) are model parameters that govern how corn yield responds to water use.

@@

Three different sets of the distribution of \(\eta\) are considered that vary in the degree of heterogeneity in \(\eta\): low, medium, and high. For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)), meaning that water use estimation is ubiased. A sample of the empirical (realized) distribution of \(\eta\) for each of the sets is presented in Figure \ref{fig:dist-eta}.

\subsection{Water use under quota and trading systems}\label{water-use-under-quota-and-trading-systems}

Under both water and proxy quota systems without trading, the same amount of quota is allocated to all the farmers. (this is realistic with insufficient information available to the administrator). For a given water quota of \(\overline{w}\), farmer \(i\)'s water use would be \(min\{w^*, \overline{w}\}\). Under the proxy quota system, the same amount of proxy quota (\(\overline{p}\)) is allocated to all the farmers. However, the effective limit on water use varies by farmer. Given the proxy quota of \(\overline{p}\), the effective water use limit for farmer \(i\) is \(\overline{p} / \eta_i\), and uses \(min\{w^*, \overline{p} / \eta_i\}\).

@@

@@

@@

The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at the \href{https://github.com/tmieno2/Measurement-Error-Water-Management}{following GitHub repository}.
